Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-12 outputs/paper/paper.qmd
update

This paper utilized a replication package of the original study and employed a cleaned data CSV file to reproduce the related figures and tables. This approach enabled us to draw correlations between the dataset and

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-polscatter-graph
#| fig-cap: "Trend in US Birth Rates with political party in their presidential mandate"

@@

@fig-polscatter-graph draw multiple trend lines

@@

## Accounting for bias

>>>>

This paper utilized a replication package of the original study and employed a cleaned data CSV file to reproduce the related figures and tables. This approach enabled us to draw correlations between the dataset and socio-cultural asepcts including abortion, contraceptive use, financial stability, religion, culture.

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-polscatter-graph
#| fig-cap: "Trend in US Birth Rates during their presidential mandate"

@@

@fig-polscatter-graph draw multiple trend lines in US birth rates during their presidential mandate. It also indicates their political party, blue represents the democrat while red presents the republican. Radican drop while republican period is seen from the analysis while democrat presidential mandate period illustrates relatively moderate delicining tendency.

@@
